Analysis of cloud enhancement events in a 30-year record of global solar irradiance at Thessaloniki, Greece

### 2024-09-08 article/article.Rmd
Commit 2024-09-08 13:09

The variable parameters of LUT consists of the month along with the relevant seasonal atmospheric profile,
the climatological values of the alpha, beta parameters of the Ångström
equation for 500nm derived from the 340nm, the WC and the SZA of the simulation.

@@

<!-- Lookup table -->
<!-- 
To create a look-up table, that aligns with our dataset, we applied some adjustments.
To account for the Sun's variability, in our one-minute GHI measurements, we adapted
each modeled value by scaling the model's input spectrum integral, to the
corresponding TSI, provided by NOAA [@Coddington2005].  Also,
we account for the effect of the Earth -- Sun distance on the irradiance, by using
the distance calculated by the Astropy [@AstropyCollaboration2022] software library.
As needed, we interpolate the resulting irradiances to the SZA of our
measurements.  For each period of the year, we used the appropriate atmospheric
profile (afglms or afglmw).  Finally, we calculated the cloud-free irradiance value at
the horizontal plane.  Thus, we were able to emulate different atmospheric condition
and levels of atmospheric clearness for the climatological conditions of the site.
With this method, the modeled cloud-free irradiances can be directly compared to each
measured one-minute value of GHI, for different conditions of atmospheric clearness.
-->

>>>>

@@

<!-- Lookup table -->
**to edit**

The variable parameters of LUT consists of the month along with the relevant seasonal
atmospheric profile, the climatological values of the alpha, beta parameters of the
Ångström equation for 500nm derived from the 340nm, the WC, with the perturbation as
described above, and the SZA of the simulation.

For the application of  the LUT, to account for the Sun's variability, in our
one-minute GHI measurements, we adapted each modeled value by scaling the model's
input spectrum integral, to the corresponding TSI, provided by NOAA
[@Coddington2005].  Also, we account for the effect of the Earth -- Sun distance on
the irradiance, by using the distance calculated by the Astropy
[@AstropyCollaboration2022] software library.  As needed, we interpolate the
resulting irradiances to the SZA of our measurements.  For each period of the year,
we used the appropriate atmospheric profile (afglms or afglmw).  Finally, we
calculated the cloud-free irradiance value at the horizontal plane.  With this
method, the modeled cloud-free irradiances schemes can be directly compared to each
measured one-minute value of GHI.
